\section{Background and History}
3D animation can be a painstakingly tedious activity. Even professional animators go through a long process to create their desired final animation. Key frames are set positions that define the start and end points of a movement, sequences of poses in time. Animators assign key frames to certain frames over time, so that in-between motions can be generated. To get an accurate animation, artists usually must assign many key frames, then spend time adjusting and editing them to be more precise. The fact that industry professionals take so much time and effort to do this shows that for an amateur or untrained artist, creating good 3D animation is close to impossible.

Researchers in the IMAGINE group at INRIA (in Grenoble, France) have noticed this problem. They have made significant progress on a project called ERC Expressive, where they aim to offer more intuitive tools to create 3D digital content. The IMAGINE team has invented a technique for animation called space-time sketching, in which a user can draw a line in the path they want a model to take and it will be animated accordingly. Their system currently supports creating movements with the path such as bouncing, rolling, and twisting. 

Because IMAGINE's tool is a comprehensive system that has not yet been released, we want to develop a smaller version of this functionality within a plug-in for the game engine, Unity. One of the main goals of the IMAGINE team's research is to make animation more accessible to the general public. We share this goal, and want to narrow it down specifically to game developers. Many game developers (both amateur and professional) use Unity to make successful games, but some lack the artistic training to integrate high quality animations easily. Our plug-in aims to alleviate this task using INRIA's space-time sketching technique.